Efficient Computation of Extended Sources

### 2022-03-29 repro/papers/sseprecond/paper.tex
test commit
added some figs

As is well-known, local optimization methods are the only feasible
approach given the dimensions of a typical instance of \ref{eqn:fwi},
and those have a tendency to stall due to ``cycle-skipping''. See for
exampe \cite{VirieuxOperto:09} and many references cited there. Source
extension is one approach to avoiding this problem. It consists in
imposing the wave equation as a soft as opposed to hard constraint, by
allowing the source field $\bff$ to have more degrees of freedom than
is permitted by a faithful model model of the seismic experiment, and
constraining these additional degrees of freedom by means of an
additive penalty modifying the probem \ref{eqn:ols}:
\begin{equation}
\label{eqn:esi}
\mbox{choose } {\bf c}, \bff \mbox{ to minimize } \|PL[{\bf c}]^{-1}\bff -d \|^2 + \alpha^2 \|A\bff\|^2 
\end{equation}
The operator $A$ penalizes deviation from known (or assumed)
characteristics of the source function - its null space consists of
feasible (or ``physical'') source models.

@@

@@

@@

@@

\plot{ddiffprednshsrecphh0}{width=\textwidth}{Plot of difference 
  between data shown in Figures \ref{fig:drecphh0} and 
  \ref{fig:dpredhsrecphh0}, plotted on same color scale as the latter 
  two figures.}

>>>>

As is well-known, local optimization methods are the only feasible
approach given the dimensions of a typical instance of \ref{eqn:fwi},
and those have a tendency to stall due to ``cycle-skipping''. See for
example \cite{VirieuxOperto:09} and many references cited there. Source
extension is one approach to avoiding this problem. It consists in
imposing the wave equation as a soft as opposed to hard constraint, by
allowing the source field $\bff$ to have more degrees of freedom than
is permitted by a faithful model model of the seismic experiment, and
constraining these additional degrees of freedom by means of an
additive penalty modifying the probem \ref{eqn:ols}:
\begin{equation}
\label{eqn:esi}
\mbox{choose } {\bf c}, \bff \mbox{ to minimize } \|PL[{\bf c}]^{-1}\bff -d \|^2 + \alpha^2 \|A\bff\|^2 
\end{equation}
The operator $A$ penalizes deviation from known (or assumed)
characteristics of the source function - its null space consists of
feasible (or ``physical'') source models.

@@

\plot{dfwdvzlh0}{width=\textwidth}{Vertical velocity gather, generated 
  with a pressure source in the lens model, 
  corresponding to pressure gather \ref{fig:dfwdphh0}.}

@@

\plot{daltvzlh0}{width=\textwidth}{Vertical velocity gather, generated 
  with a velocity source in the lens model, corresponding to 
  pressure gather \ref{fig:daltphh0}.}

@@

\plot{dsvcomplh0}{width=\textwidth}{Difference between velocity gathers
  shown in Figures \ref{fig:dfwdvzlh0} and \ref{fig:daltvzlh0},
  plotted on the same color scale as these figures.}

@@

\plot{dprednshsrecpll0}{width=\textwidth}{Pressure gather at receiver
  datum $z=z_r=1000$ m simulated from source gather shown in Figure
  \ref{fig:preddnshshh0}. Compare with point source pressure gather
  (Figure \ref{fig:drecplh0}).}

\plot{ddiffprednshsrecphh0}{width=\textwidth}{Plot of difference 
  between data shown in Figures \ref{fig:drecphh0} and 
  \ref{fig:dprednshsrecphh0}, plotted on same color scale as the latter 
  two figures.}

\plot{ddiffprednshsrecpll0}{width=\textwidth}{Plot of difference 
  between data shown in Figures \ref{fig:drecplh0} and 
  \ref{fig:dprednshsrecplh0}, plotted on same color scale as the latter 
  two figures.}
